The unphysicality of Hilbert spaces

### 2023-08-12 Articles/2023-HilbertQuantum/HilbertQuantum.tex
Added last reference

The Schwartz space has several other interesting properties,\cite{moretti_spectral_2017, reed_methods_1980, hall_quantum_2013} explored in more detail in the appendix. For example:

>>>>

The Schwartz space has several other interesting properties,\cite{moretti_spectral_2017, reed_methods_1980, hall_quantum_2013, rauch_solution_1991} explored in more detail in the appendix. For example:
